% =============================================================================
%  Academic Research Matrix: Cosmological Parsimony
%  Author: Rafael D. De Paz
% =============================================================================
\documentclass[12pt, a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath, amssymb, amsthm, mathtools}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{natbib}

\geometry{margin=1in}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{assumption}[theorem]{Assumption}

\hypersetup{colorlinks=true,linkcolor=cyan,citecolor=cyan,urlcolor=cyan}


\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}
\usepackage{draftwatermark}
\SetWatermarkText{SOVEREIGN PROTOCOL // ID: 8A01159}
\SetWatermarkScale{0.5}
\SetWatermarkLightness{0.94}
\begin{document}

\title{\textbf{Occam-Decoherence: Parsimony as a Physical Thermodynamic Limit}}
\author{Rafael D. De Paz \\ \textit{Systems Architect} \\ \texttt{me@rdepaz.com}}
\date{2026-03-23}
\maketitle

\begin{abstract}
Occam's Razor is heavily utilized as a philosophical heuristic in cosmological formulation. We redefine it entirely as a hard mathematical and information-processing limit constraints: Cosmological Parsimony. This paper constructs a mathematical framework demonstrating that physical space natively forces wave-function collapse and state deletion when localized reality arrays exceed defined maximum computation densities. I prove mathematically that nature does not maintain infinite computational branch possibilities; instead, utilizing strict algorithmic tensor limits, it triggers immediate probability reduction to preserve geometric reality structure.
\end{abstract}

\vspace{0.5em}
\noindent\textbf{Keywords:} Wave-function Collapse, Occam's Razor, Matrix Computation limits, Decoherence.

\vspace{0.5em}
\noindent\textbf{2026 MSC:} 83F05, 82C32, 68Q80, 11Z05.

% =============================================================================
\section{Algorithmic Formalization of Information Compression}
% =============================================================================
Within bounded system models, local regions encode maximum entropy processing rates \cite{shannon1948mathematical}. As chaotic probability chains (such as atomic entanglements geometry) interact with macro-variables, information complexity geometrically outpaces the operational grid bounds \cite{lamport1978time}.

\begin{theorem} [Matrix Pruning Action]
For any physical state $\mathcal{S}$, when the Shannon description scale length $L(\mathcal{S})$ breaches the bounds $K_{max}$, algorithmic resolution automatically reduces the equation down to the state requiring the absolute minimum energy cost requirement to simulate.
\begin{equation}
    \min_{E}( \mathcal{S}_{reduction} ) = C_{0}
\end{equation}
\end{theorem}
Occam's heuristic operates therefore not out of aesthetic choice, but out of absolute mathematically enforced universal bandwidth limits \cite{turing1936computable}.

% =============================================================================
\section{Conclusion}
% =============================================================================
Physical reality operates using active Cosmological Parsimony models—crushing exponential branches of probability strictly to conserve $O(1)$ stability in a discrete system.

% =============================================================================
% References
% =============================================================================
\bibliographystyle{plainnat}
\bibliography{references}

\vspace{3em}
\noindent\hrulefill

\end{document}