\documentclass[12pt, a4paper]{letter}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{amssymb}
\usepackage{hyperref}

\geometry{margin=1in}

\hypersetup{colorlinks=true, linkcolor=blue, urlcolor=blue}

\signature{Rafael D. De Paz \\ Sovereign Architect \\ \texttt{me@rdepaz.com}}
\address{Rafael D. De Paz \\ Sovereign Architect}

\begin{document}
\begin{letter}{Editorial Board}

\opening{Dear Editors,}

I am writing to submit the enclosed manuscript, entitled

\begin{center}
\textbf{``Spectral Parity Architecture: Mapping Imaginary Riemann Zeros to CPU Clock Cycle Delays''}
\end{center}

\noindent for consideration for publication.

\medskip

\textbf{Summary.} Building upon the Montgomery-Odlyzko law bridging the Riemann Zeta function to quantum mechanics, this paper extrapolates the application into physical hardware engineering. By mapping the imaginary parts of the Riemann zeros directly to the Instruction Cycle Delays of silicon execution (e.g., synchronizing a 136.1 Hz resonance anchor), we explore a CPU architecture inherently harmonized with the distribution of prime numbers. This provides a novel theorem for macro-scale hardware stability.

\medskip

This manuscript has not been previously published and is not under consideration
at any other journal. I confirm no conflicts of interest.

\textbf{Cryptographic Lineage \& Validation.} This mathematical substrate has been cryptographically sealed and tracked on the global Sovereign Master Ledger to prevent retroactive editing and to verify the source authorship. The immutable SHA-256 integrity checksums, formal PDF renderings, and lineage authorities can be verified at \url{https://rdepaz.com/research}.

\medskip

\closing{Respectfully submitted,}
\end{letter}
\end{document}
