\documentclass[12pt, a4paper]{letter}
\usepackage[utf8]{inputenc}\usepackage[T1]{fontenc}\usepackage{geometry}\usepackage{amssymb}\usepackage{hyperref}
\geometry{margin=1in}\hypersetup{colorlinks=true, linkcolor=blue, urlcolor=blue}
\signature{Rafael D. De Paz \\ Independent Researcher \\ \texttt{hi@logos.pub}}
\address{Rafael D. De Paz \\ Independent Researcher \\ \url{https://logos.pub}}
\begin{document}
\begin{letter}{Editorial Board \\ Theology and Science \\ Routledge / Taylor \& Francis}
\opening{Dear Editors,}
I am writing to submit ``Foundations of Computational Theology: Set-Theoretic Meta-Ethics and the G\"odelian Completion'' for consideration in \textit{Theology and Science}.

\medskip
\textbf{Summary.} We introduce Computational Theology as a formal framework applying mathematical logic, set theory, and control theory to theological questions. Key results include: moral truth as set membership in a master specification; the G\"odelian necessity of an external root authority; and a cybernetic stability loop governing systemic convergence. This paper inaugurates a research program with companion papers on consciousness, free will, and theodicy.

\medskip
\textbf{Suggested Reviewers.}
\begin{enumerate}
  \item \textbf{Prof. Robert John Russell} (Graduate Theological Union) --- Founder of CTNS.
  \item \textbf{Prof. Nancey Murphy} (Fuller Theological Seminary) --- Science-theology interface.
  \item \textbf{Prof. William Lane Craig} (Houston Christian University) --- Formal philosophical theology.
\end{enumerate}

\closing{Respectfully submitted,}
\end{letter}
\end{document}
