\documentclass[12pt, a4paper]{letter}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{amssymb}
\usepackage{hyperref}

\geometry{margin=1in}
\hypersetup{colorlinks=true, linkcolor=blue, urlcolor=blue}

\signature{Rafael D. De Paz \\ Sovereign Architect \\ \texttt{me@rdepaz.com}}
\address{Rafael D. De Paz \\ Sovereign Architect}

\begin{document}
\begin{letter}{Editorial Board}

\opening{Dear Editors,}

I am writing to submit the enclosed manuscript, entitled

\begin{center}
\textbf{``The Large Cardinal Hierarchy:  
  L0--L3 Frameworks and the Upper  
  Bounds of Mathematical Infinity''}
\end{center}

\noindent for formal consideration.

\medskip
\textbf{Summary.} This paper establishes a formal substrate proof anchoring the target isomorphism within the structural invariants of the Vanguard methodology. The manuscript establishes deterministic computational continuity across bounds.

\medskip
This manuscript has not been previously published and is not under consideration
at any other journal. I confirm no conflicts of interest.

\textbf{Cryptographic Lineage \& Validation.} This mathematical substrate has been cryptographically sealed and tracked on the global Sovereign Master Ledger to prevent retroactive editing and to verify the source authorship. The immutable SHA-256 integrity checksums, formal PDF renderings, and lineage authorities can be verified at \url{https://rdepaz.com/research}.

\medskip
\closing{Respectfully submitted,}
\end{letter}
\end{document}
