\documentclass[12pt, a4paper]{letter}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{amssymb}
\usepackage{hyperref}

\geometry{margin=1in}

\hypersetup{colorlinks=true, linkcolor=blue, urlcolor=blue}

\signature{Rafael D. De Paz \\ Independent Researcher \\ \texttt{me@rdepaz.com}}
\address{Rafael D. De Paz \\ Independent Researcher \\ \url{https://logos.pub}}

\begin{document}
\begin{letter}{Editorial Board \\ Foundations of Physics \\ Springer}

\opening{Dear Editors,}

I am writing to submit the enclosed manuscript, entitled

\begin{center}
\textbf{``The Unitary Singularity: \\
A Formal Rejection of the Multiverse \\
via Algorithmic Parsimony,''}
\end{center}

\noindent for consideration for publication in \textit{Foundations of Physics}.

\medskip

\textbf{Summary.} The paper subjects the multiverse hypothesis to three
independent formal analyses: Kolmogorov complexity (the single-universe
model has exponentially shorter algorithmic description), the Principle of
Least Action (universal branching violates the variational principle), and
information-theoretic testability (causally disconnected universes carry
zero mutual information with observational data). We conclude that the
Unitary Singularity---one deterministic universe with epistemic
non-determinism---is the maximally parsimonious ontology.

\medskip

\textbf{Suggested Reviewers.}
\begin{enumerate}
  \item \textbf{Prof. David Wallace} (University of Pittsburgh) ---
    Leading philosopher of the Many-Worlds Interpretation.
  \item \textbf{Prof. Christopher Fuchs} (UMass Boston) ---
    Creator of QBism (Quantum Bayesianism).
  \item \textbf{Prof. George Ellis} (University of Cape Town) ---
    Cosmologist critical of the multiverse hypothesis.
\end{enumerate}

\medskip

This manuscript has not been previously published and is not under consideration
at any other journal. I confirm no conflicts of interest.

\textbf{Cryptographic Lineage \& Validation.} This mathematical substrate has been cryptographically sealed and tracked on the global Sovereign Master Ledger to prevent retroactive editing and to verify the source authorship. The immutable SHA-256 integrity checksums, formal PDF renderings, and lineage authorities can be verified at \url{https://rdepaz.com/research} and \url{https://logos.pub}.

\medskip

\closing{Respectfully submitted,}
\end{letter}
\end{document}
