\documentclass[12pt, a4paper]{letter}
\usepackage[utf8]{inputenc}\usepackage[T1]{fontenc}\usepackage{geometry}\usepackage{amssymb}\usepackage{hyperref}
\geometry{margin=1in}\hypersetup{colorlinks=true, linkcolor=blue, urlcolor=blue}
\signature{Rafael D. De Paz \\ Independent Researcher \\ \texttt{me@rdepaz.com}}
\address{Rafael D. De Paz \\ Independent Researcher \\ \url{https://logos.pub}}
\begin{document}
\begin{letter}{Editorial Board \\ Philosophy of Science \\ University of Chicago Press}
\opening{Dear Editors,}
I submit ``Epistemological Triage: A Bayesian Framework for the Evaluation of Extraordinary Claims'' for consideration in \textit{Philosophy of Science}.

\medskip
\textbf{Summary.} We formalize Sagan's dictum into a rigorous Bayesian triage framework. We define claim extraordinariness as negative log-prior, derive that the evidence threshold scales exponentially with surprisal, and construct a four-level triage matrix based on Type I/II error cost asymmetry. Applications span medical diagnosis, intelligence analysis, the scientific replication crisis, and anomalous aerial phenomena.

\medskip
\textbf{Suggested Reviewers.}
\begin{enumerate}
  \item \textbf{Prof. Stephan Hartmann} (LMU Munich) --- Bayesian epistemology and philosophy of science.
  \item \textbf{Prof. James Hawthorne} (University of Oklahoma) --- Confirmation theory and inductive logic.
  \item \textbf{Prof. Kevin McCain} (University of Alabama) --- Evidentialism and epistemic warrant.
\end{enumerate}

\textbf{Cryptographic Lineage \& Validation.} This mathematical substrate has been cryptographically sealed and tracked on the global Sovereign Master Ledger to prevent retroactive editing and to verify the source authorship. The immutable SHA-256 integrity checksums, formal PDF renderings, and lineage authorities can be verified at \url{https://rdepaz.com/research} and \url{https://logos.pub}.

\medskip

\closing{Respectfully submitted,}
\end{letter}
\end{document}
