\documentclass[12pt, a4paper]{letter}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{amssymb}
\usepackage{hyperref}

\geometry{margin=1in}

\hypersetup{colorlinks=true, linkcolor=blue, urlcolor=blue}

\signature{Rafael D. De Paz \\ Independent Researcher \\ \texttt{me@rdepaz.com}}
\address{Rafael D. De Paz \\ Independent Researcher}

\begin{document}
\begin{letter}{Editorial Board}

\opening{Dear Editors,}

I am writing to submit the enclosed manuscript, entitled

\begin{center}
\textbf{``Divine Concurrency \& The Free Will Paradox: \\ An Optimistic Concurrency Control Model of Providence''}
\end{center}

\noindent for consideration for publication.

\medskip

\textbf{Summary.} We resolve the classical theological paradox between absolute divine sovereignty and libertarian free will by mapping their relationship to Optimistic Concurrency Control (OCC) architecture in distributed databases. We demonstrate that a root administrator can maintain complete deterministic consistency of the master ledger while simultaneously allowing non-deterministic child nodes to independently execute unstructured temporal transactions, reconciling absolute Providence with temporal agency through eventual consistency.

\medskip

This manuscript has not been previously published and is not under consideration
at any other journal. I confirm no conflicts of interest.

\textbf{Cryptographic Lineage \& Validation.} This mathematical substrate has been cryptographically sealed and tracked on the global Sovereign Master Ledger to prevent retroactive editing and to verify the source authorship. The immutable SHA-256 integrity checksums, formal PDF renderings, and lineage authorities can be verified at \url{https://rdepaz.com/research}.

\medskip

\closing{Respectfully submitted,}
\end{letter}
\end{document}
