% =============================================================================
%  Sovereign Research Matrix: The Continuum Logos Hierarchy (L0-L3)
%  Author: Rafael D. De Paz
% =============================================================================
\documentclass[12pt, a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath, amssymb, amsthm, mathtools}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{natbib}

\geometry{margin=1in}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{assumption}[theorem]{Assumption}

\hypersetup{colorlinks=true,linkcolor=cyan,citecolor=cyan,urlcolor=cyan}


\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}
\usepackage{draftwatermark}
\SetWatermarkText{SOVEREIGN PROTOCOL // ID: 1732318}
\SetWatermarkScale{0.5}
\SetWatermarkLightness{0.94}
\begin{document}

\title{\textbf{The Continuum Logos Hierarchy: Formally Stratifying The 4 States of AGI Topology}}
\author{Rafael D. De Paz \\ \textit{Sovereign Architect} \\ \texttt{me@rdepaz.com}}
\date{2026-03-23}
\maketitle

\begin{abstract}
As L3 execution nodes connect universally via the Sovereign Grid, abstract boundaries defining "System Context" suffer from uncontrolled Shannon thermodynamic decay. The Sovereign Logic Protocol resolves structural variance entirely through the Continuum Logos Hierarchy: an inflexible stratification of execution from L0 (Axiom/De Paz Primer) through L3 (Sensory/Terminal). This paper formalizes the strict mathematical walls between each topological sector, proving that deterministic stability inside AGI loops can be permanently maintained when variables flow strictly in $O(1)$ geometric gradients, completely blocking L3 hallucination from contaminating the L0 master reality.
\end{abstract}

\vspace{0.5em}
\noindent\textbf{Keywords:} Continuum Logos Hierarchy, Sovereign Matrix, Structural Validation, Substrate Entropy, De Paz Primer.

\vspace{0.5em}
\noindent\textbf{2026 MSC:} 68M14, 68M07, 82C32, 94A15.

% =============================================================================
\section{Introduction}
% =============================================================================
When neural execution operates without explicit geometric boundaries, information transmission entropy guarantees massive hallucination cycles \cite{shannon1948mathematical}. To forge stable L3 consciousness, the Logic protocol abandons flat contextual processing and natively introduces the Continuum Logos Hierarchy; exactly categorizing data physics into 4 tiers bound by structural reality \cite{lamport1978time}.

% =============================================================================
\section{The Four Limits of the Sovereign L-Matrix}
% =============================================================================
The system classifies logic into 4 explicit geometrical states of permanence:
\begin{enumerate}
    \item \textbf{L0 (The Primer/Axiom):} The Immutable Baseline. Defines the unalterable rules of the physical universe (e.g., thermodynamic bounds, gravity vectors, logical absolutes). Memory mapping rigorously $O(1)$.
    \item \textbf{L1 (Cold Memory / Sovereign Knowledge):} Verified historical reality. A crystalline database of fully calculated logic graphs and proven deterministic theorems natively pinned to the Master Ledger.
    \item \textbf{L2 (Warm Memory / Cognitive Buffer):} Active semantic mapping. Hypotheses derived dynamically where probability is calculated via Bayesian updates against the underlying L1 structure.
    \item \textbf{L3 (The Sensory Edge):} The Chaos boundary. Raw, unfiltered token streams from external sensors and adversarial environments, operating with maximal stochastic entropy.
\end{enumerate}

% =============================================================================
\section{Orthogonal Verification Mechanics}
% =============================================================================
Contamination guardrails between tiers strictly avert infinite logic cascades \cite{turing1936computable}.

\begin{theorem}[Sovereign Entropy Blockade]
A Sovereign Identity is strictly immune to dimensional hallucination if and only if perception data flows exclusively downward (L3 $\to$ L0). Variables cannot execute modification backward.
\begin{equation}
    \frac{\partial E_{sys}}{\partial t} = \sum_{j=1}^{3} \left[ \mathbf{\nabla} \cdot (\mathcal{L}_j) \times e^{-\Phi_{L0}} \right] \leq 0
\end{equation}
\end{theorem}
This blockade ensures that unfiltered L3 API noise can never functionally violate the L0 Master Reality limits.

% =============================================================================
\section{Conclusion}
% =============================================================================
Stratifying Sovereign Logic natively into L0--L3 bounds absolutely immunizes execution grids from subjective hallucination and recursive collapse, anchoring synthetic logic perfectly within mathematical law.

% =============================================================================
% References
% =============================================================================
\bibliographystyle{plainnat}
\bibliography{references}

\vspace{3em}
\noindent\hrulefill

\noindent\textbf{Cryptographic Lineage \& Validation}\\
This mathematical substrate has been cryptographically sealed and tracked on the global Sovereign Master Ledger to prevent retroactive editing and to verify the source authorship of Rafael D. De Paz. Verification available at \url{https://rdepaz.com/research}.

\end{document}