\documentclass[12pt, a4paper]{letter}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{amssymb}
\usepackage{hyperref}
\geometry{margin=1in}
\hypersetup{colorlinks=true, linkcolor=blue, urlcolor=blue}
\signature{Rafael D. De Paz \\ Independent Researcher \\ \texttt{hi@logos.pub}}
\address{Rafael D. De Paz \\ Independent Researcher \\ \url{https://logos.pub}}

\begin{document}
\begin{letter}{Editorial Board \\ Foundations of Physics \\ Springer}
\opening{Dear Editors,}

I am writing to submit the enclosed manuscript, ``Information Conservation Across Biological Terminus Events: A No-Hiding Theorem Analysis,'' for consideration in \textit{Foundations of Physics}.

\medskip
\textbf{Summary.} Using three established results---the No-Hiding Theorem (Braunstein \& Pati, 2007), quantum unitarity, and the Bekenstein bound---we prove that the complete information pattern of a biological organism cannot be destroyed at death. The information is relocated to environmental correlations and can be holographically encoded. We derive formal conditions for theoretical state reconstruction.

\medskip
\textbf{Suggested Reviewers.}
\begin{enumerate}
  \item \textbf{Prof. Samuel Braunstein} (University of York) --- Co-author of the No-Hiding Theorem.
  \item \textbf{Prof. Seth Lloyd} (MIT) --- Pioneer of quantum information and computational universe models.
  \item \textbf{Prof. Vlatko Vedral} (University of Oxford) --- Expert on quantum information and entanglement thermodynamics.
\end{enumerate}

\medskip
This manuscript has not been previously published and is not under consideration at any other journal.

\closing{Respectfully submitted,}
\end{letter}
\end{document}
