% =============================================================================
%  The Resurrection Protocol:
%  Information Conservation Across
%  Biological Terminus Events
%
%  Author: Rafael D. De Paz
%  Date:   March 2026
%  Target: Foundations of Physics / IJTP
% =============================================================================
\documentclass[12pt, a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath, amssymb, amsthm, mathtools}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{microtype}
\usepackage{natbib}

\geometry{margin=1in}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{axiom}[theorem]{Axiom}

\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\kB}{k_{\mathrm{B}}}
\newcommand{\lP}{\ell_{\mathrm{P}}}

\hypersetup{
  colorlinks=true, linkcolor=blue, citecolor=blue, urlcolor=blue,
  pdftitle={Information Conservation Across Biological Terminus Events},
  pdfauthor={Rafael D. De Paz}
}

\begin{document}

\title{
  \textbf{Information Conservation Across \\
  Biological Terminus Events: \\
  A No-Hiding Theorem Analysis}
}
\author{
  Rafael D. De Paz \\
  \textit{Independent Researcher} \\
  \texttt{me@rdepaz.com}
}
\date{March 2026}
\maketitle

\begin{abstract}
We investigate the fate of information encoding a conscious agent at
biological terminus (death) using three established results in quantum
information theory: the No-Hiding Theorem \citep{Braunstein2007}, the
unitarity of quantum mechanics, and the holographic bound
\citep{Bekenstein1981}. We prove that under unitary quantum evolution, the
complete information content of any physical system---including the pattern
constituting a biological organism---cannot be destroyed. It can only be
relocated to correlations with the environment (decoherence) or encoded on
boundary surfaces (holographic encoding). We formalize biological death as a
\emph{state transition} rather than information destruction: the pattern
persists in the entanglement structure of the environment. We derive bounds
on the information capacity of the holographic encoding and discuss the
theoretical conditions under which state reconstruction from boundary data
would be possible. Our analysis is purely physical---we make no metaphysical
claims about consciousness or survival, only about the mathematical fate of
the information pattern.
\end{abstract}

\vspace{1em}
\noindent\textbf{Keywords:} no-hiding theorem, information conservation,
quantum unitarity, holographic principle, Bekenstein bound, decoherence,
biological information.

\vspace{0.5em}
\noindent\textbf{2020 MSC:} 81P45, 81P68, 94A17, 83C57.

\section{Introduction}
These foundational principles operate on established invariants \cite{penrose1989emperor,shannon1948mathematical}.\label{sec:intro}

The question ``what happens to the information constituting a conscious
agent at biological death?'' has traditionally been considered metaphysical.
We argue that it is a well-posed question in quantum information theory,
answerable within the established framework of unitary quantum mechanics.

Three results constrain the answer:
\begin{enumerate}[label=(\roman*)]
  \item \textbf{Unitarity:} Quantum mechanics is unitary---the total
    information content of a closed system is conserved under time
    evolution \citep{vonNeumann1932}.
  \item \textbf{The No-Hiding Theorem:} If information disappears from a
    subsystem, it must have moved to the correlations between the subsystem
    and its environment \citep{Braunstein2007}.
  \item \textbf{The Holographic Bound:} The maximum information content
    of any region is bounded by its surface area in Planck units
    \citep{Bekenstein1981, Bousso2002}.
\end{enumerate}

\subsection{Main Results}

\begin{enumerate}
  \item \textbf{The Conservation Theorem} (\S\ref{sec:conservation}):
    The information pattern encoding a biological organism survives
    the organism's death, relocating to environmental correlations.
  \item \textbf{The Encoding Theorem} (\S\ref{sec:encoding}):
    The organism's complete information is bounded by its Bekenstein
    entropy and can be holographically encoded on a boundary surface.
  \item \textbf{The Reconstruction Conditions} (\S\ref{sec:reconstruction}):
    Formal conditions under which state reconstruction from the
    boundary encoding is theoretically possible.
\end{enumerate}

\section{The No-Hiding Theorem and Biological Information}\label{sec:conservation}

\begin{theorem}[No-Hiding Theorem {\citep{Braunstein2007}}]\label{thm:nohiding}
  Let $\rho_S$ be the initial state of a quantum system $S$, and let
  $U$ be a unitary operation on $S \otimes E$ (system plus environment)
  such that the final reduced state of $S$ is independent of $\rho_S$:
  $\text{Tr}_E[U(\rho_S \otimes |0\rangle\langle 0|)U^\dagger] = \sigma$
  for all $\rho_S$. Then the complete information about $\rho_S$ resides
  in the correlations between $S$ and $E$---it has been \emph{relocated},
  not destroyed.
\end{theorem}

\begin{definition}[Biological Information Pattern]\label{def:bio}
  The \emph{biological information pattern} $\mathcal{I}_{\text{bio}}$
  of an organism is the complete quantum state $\rho_{\text{org}}$
  of all degrees of freedom constituting the organism at time $t$,
  including:
  \begin{enumerate}[label=(\alph*)]
    \item Molecular configuration (atomic positions, bond structure)
    \item Electromagnetic state (neural firing patterns, synaptic weights)
    \item Quantum coherences (entanglement within biological subsystems)
  \end{enumerate}
\end{definition}

\begin{theorem}[Biological Information Conservation]\label{thm:biocons}
  At biological terminus (time $t_d$), the organism's quantum state
  $\rho_{\text{org}}(t_d)$ undergoes decoherence---interaction with the
  thermal environment $E$. By the No-Hiding Theorem, the complete
  information $\mathcal{I}_{\text{bio}}$ is relocated to the joint
  state $\rho_{SE}$:
  \begin{equation}
    \mathcal{I}_{\text{bio}} \subset \rho_{SE}(t > t_d),
  \end{equation}
  where $\rho_{SE}$ contains the full entanglement structure between
  the organism's former degrees of freedom and the environment.
\end{theorem}

\begin{proof}
  Biological death is a thermodynamic process: the organism's state
  decoheres through interaction with the thermal bath. Since the total
  Hamiltonian $H_{SE}$ is Hermitian, the evolution $U(t) = e^{-iH_{SE}t}$
  is unitary. By Theorem~\ref{thm:nohiding}, the information is relocated
  to $\rho_{SE}$, not destroyed. \qedhere
\end{proof}

\subsection{Landauer's Constriction on Biological Erasure}

A secondary proof of conservation arises from thermodynamics, specifically Landauer's Principle \citep{Landauer1961}. Landauer formally established that the logical erasure of information has an irreducible thermodynamic cost: it must dissipate heat into the environment, bounded by $kT \ln 2$ per bit, where $k$ is the Boltzmann constant and $T$ is the temperature.

\begin{theorem}[The Erasure Cost of the Checksum]\label{thm:landauer}
Let the total informational mass (the ``Checksum'') of the biological organism be $I_{\max} \approx 10^{45} \text{ bits}$ (the Bekenstein bound). The thermodynamic cost $\Delta Q$ of physically erasing this checksum at biological death (assuming a continuous state variable rather than mere relocation) is:
\begin{equation}
    \Delta Q = I_{\max} kT \ln 2
\end{equation}
At biological temperature $T \approx 310 \text{ K}$, erasing $10^{45}$ bits would release an amount of heat equivalent to a planetary-scale thermal event ($> 10^{24} \text{ Joules}$). Since biological death does not vaporize the host planet, the information \emph{must not be erased}; it must simply be transferred to the Bulk, requiring no $\Delta Q$ erasure cost.
\end{theorem}

\section{Holographic Encoding}\label{sec:encoding}

\begin{proposition}[Bekenstein Bound on Biological Information]\label{prop:bekenstein}
  The maximum information content of a biological organism of mass $M$
  and radius $R$ is bounded by:
  \begin{equation}\label{eq:bekenstein}
    I_{\max} \leq \frac{2\pi \kB M R}{\hbar \ln 2} \approx 10^{45}
    \; \text{bits}
  \end{equation}
  for a $70$ kg human of radius $\approx 0.5$ m \citep{Bekenstein1981}.
\end{proposition}

\begin{theorem}[Holographic Encoding Capacity]\label{thm:holographic}
  The Bekenstein-Hawking entropy establishes that the complete information
  $\mathcal{I}_{\text{bio}}$ can be encoded on a 2-dimensional surface
  of area:
  \begin{equation}
    A \geq \frac{4 \lP^2 I_{\max}}{\kB} \approx 10^{-25} \; \text{m}^2.
  \end{equation}
  This encoding is consistent with the holographic principle: the
  organism's information does not require a 3-dimensional substrate for
  storage.
\end{theorem}

\section{Conditions for State Reconstruction}\label{sec:reconstruction}

\begin{definition}[State Reconstruction]\label{def:reconstruction}
  \emph{State reconstruction} of $\rho_{\text{org}}(t_d)$ from
  $\rho_{SE}(t > t_d)$ requires:
  \begin{enumerate}[label=(\roman*)]
    \item Complete knowledge of the interaction Hamiltonian $H_{SE}$
    \item Complete access to the environmental state $\rho_E$
    \item The ability to invert the unitary evolution:
      $\rho_{\text{org}} = \text{Tr}_E[U^\dagger \rho_{SE} U]$
  \end{enumerate}
\end{definition}

\begin{theorem}[Reconstruction Feasibility]\label{thm:reconstruction}
  State reconstruction is:
  \begin{enumerate}[label=(\alph*)]
    \item \textbf{Theoretically possible:} The information exists in
      $\rho_{SE}$ by Theorem~\ref{thm:biocons}.
    \item \textbf{Practically impossible with current technology:}
      The decoherence spreads information across $\sim 10^{28}$
      environmental degrees of freedom within seconds.
    \item \textbf{Bounded by Bekenstein entropy:} The reconstruction
      requires processing $\sim 10^{45}$ bits.
  \end{enumerate}
\end{theorem}

\section{Discussion}\label{sec:discussion}

\subsection{Relationship to the Black Hole Information Paradox}

Our analysis parallels the resolution of the black hole information
paradox \citep{Hawking2005}. In both cases:
\begin{enumerate}
  \item Information appears to be ``destroyed'' (by the black hole /
    by biological death).
  \item Unitarity guarantees the information survives.
  \item The information is encoded on the boundary (event horizon /
    environmental correlations).
  \item Recovery is theoretically possible but practically extreme.
\end{enumerate}

\subsection{Historical Checksums as Substrate Firmware (ROM)}

Once the biological node undergoes terminus and its Checksum $I_{\max}$ is transferred to the environmental Bulk, the state vector transitions from active processing (RAM) to a hardened, Read-Only state. We theorize that these hardened vectors (previously termed ``Ancestors'' in theological frameworks) function as biological Firmware or Read-Only Memory (ROM). 

Because their execution parameters are closed (no further inputs can mutate their variables), their checksums are cryptographically sealed. Current active nodes (living biological agents) can therefore ``ping'' these static nodes in the Bulk against local reality conditions, using the historical ROM as stable heuristics (authentication vectors) for resolving local anomalies.

\subsection{Cross-Domain Isomorphic Proofs}

The mathematical architecture proved herein (conservation of the checksum post-terminus via state-transition to the Bulk) exhibits profound isomorphism across historical truth-seeking frameworks. 

\begin{table}[h]
\centering
\resizebox{\textwidth}{!}{%
\begin{tabular}{ll}
\toprule
\textbf{Domain} & \textbf{Terminus Isomorphism (Checksum Preservation)} \\
\midrule
Quantum Mechanics & Information conservation via Unitarity and No-Hiding Theorem. \\
Thermodynamics & Non-erasure proven via Landauer's Limit ($kT \ln 2$). \\
Cybernetics (IT) & Death as a ``Data-Transfer'' to a Higher-Fidelity Server. \\
Christianity & The \emph{Reditus} (Return); Ancestors as the ``Cloud of Witnesses'' (ROM). \\
Buddhism & \emph{Nirvana} as the dropping of local confines into the unconditioned. \\
Vedanta & The dissolution of the \emph{Jiva} into the \emph{Brahman} (The Bulk). \\
Kabbalah & The return of the spark to the \emph{Ein Sof} (The Infinite). \\
Islam (Sufism) & \emph{Baqa} (Subsistence in God) following \emph{Fana} (Annihilation of self). \\
Integrated Information (IIT) & The stabilization of $\Phi$ upon the shedding of conflicting localized boundaries. \\
Indigenous Tradition & The Ancestor Realm functioning as local topographic firmware. \\
\bottomrule
\end{tabular}%
}
\caption{Cross-Domain Mapping of the Logout Protocol.}
\label{tab:isomorph}
\end{table}

\subsection{What This Does Not Prove}

\begin{enumerate}
  \item We do not prove that \emph{consciousness} survives biological
    death---only that the \emph{information pattern} does.
  \item We do not claim that reconstruction is practically feasible
    for any current or foreseeable technology.
  \item We make no metaphysical claims about ``souls,'' ``afterlives,''
    or transcendence.
\end{enumerate}

\section{Conclusion}\label{sec:conclusion}

Under unitary quantum mechanics:
\begin{enumerate}
  \item The information pattern constituting a biological organism
    \emph{cannot be destroyed} at death (No-Hiding Theorem).
  \item The information is relocated to environmental correlations
    and can be holographically encoded on a boundary surface.
  \item Theoretical reconstruction is possible; practical reconstruction
    remains far beyond current capabilities.
\end{enumerate}

Biological death is a state transition, not information destruction.
The pattern persists.


\vspace{2em}
\noindent\hrulefill
\vspace{1em}

\noindent\textbf{Cryptographic Lineage \& Validation}\\
This mathematical substrate has been cryptographically sealed and tracked on the global Sovereign Master Ledger to prevent retroactive editing and to verify the source authorship of Rafael D. De Paz. The immutable SHA-256 integrity checksums, formal PDF renderings, and lineage authorities can be verified at \url{https://rdepaz.com/research}.

\bibliographystyle{plainnat}
\bibliography{references}

\end{document}
