\documentclass[12pt, a4paper]{letter}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{amssymb}
\usepackage{hyperref}

\geometry{margin=1in}

\hypersetup{colorlinks=true, linkcolor=blue, urlcolor=blue}

\signature{Rafael D. De Paz \\ Independent Researcher \\ \texttt{me@rdepaz.com}}
\address{Rafael D. De Paz \\ Independent Researcher \\ \url{https://logos.pub}}

\begin{document}
\begin{letter}{Editorial Board \\ Chaos, Solitons \& Fractals \\ Elsevier}

\opening{Dear Editors,}

I am writing to submit the enclosed manuscript, entitled

\begin{center}
\textbf{``Chaos, Attractors, and Determinism: \\
Local Stochasticity in Globally \\
Deterministic Systems,''}
\end{center}

\noindent for consideration for publication in \textit{Chaos, Solitons \& Fractals}.

\medskip

\textbf{Summary.} The paper establishes that local unpredictability (positive
Lyapunov exponents) and global determinism (convergence to a compact strange
attractor) are coextensive properties of dissipative nonlinear systems. We
prove predictive horizon bounds, global confinement via the Kaplan-Yorke
dimension, and ergodic coverage via Sinai-Ruelle-Bowen measures. We apply
these results to the philosophical problem of free will and determinism.

\medskip

\textbf{Suggested Reviewers.}
\begin{enumerate}
  \item \textbf{Prof. Steven Strogatz} (Cornell University) ---
    Author of \textit{Nonlinear Dynamics and Chaos}.
  \item \textbf{Prof. James Yorke} (University of Maryland) ---
    Co-discoverer of the period-doubling route to chaos.
  \item \textbf{Prof. Celso Grebogi} (University of Aberdeen) ---
    Pioneer of chaotic dynamics and fractal basin boundaries.
\end{enumerate}

\medskip

This manuscript has not been previously published and is not under consideration
at any other journal. I confirm no conflicts of interest.

\textbf{Cryptographic Lineage \& Validation.} This mathematical substrate has been cryptographically sealed and tracked on the global Sovereign Master Ledger to prevent retroactive editing and to verify the source authorship. The immutable SHA-256 integrity checksums, formal PDF renderings, and lineage authorities can be verified at \url{https://rdepaz.com/research} and \url{https://logos.pub}.

\medskip

\closing{Respectfully submitted,}
\end{letter}
\end{document}
