\documentclass[12pt, a4paper]{letter}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{amssymb}
\usepackage{hyperref}

\geometry{margin=1in}

\hypersetup{colorlinks=true, linkcolor=blue, urlcolor=blue}

\signature{Rafael D. De Paz \\ Independent Researcher \\ \texttt{me@rdepaz.com}}
\address{Rafael D. De Paz \\ Independent Researcher \\ \url{https://logos.pub}}

\begin{document}
\begin{letter}{Editorial Board \\ Theology and Science \\ Routledge / Taylor \& Francis}

\opening{Dear Editors,}

I am writing to submit the enclosed manuscript, entitled

\begin{center}
\textbf{``Theodicy as Error Handling: \\
A Computational Framework for the \\
Problem of Evil,''}
\end{center}

\noindent for consideration for publication in \textit{Theology and Science}.

\medskip

\textbf{Summary.} The paper reframes the classical Problem of Evil as a
system design problem using formal computer science. Evil is modeled as a
non-terminating recursive loop (the Halting Problem), suffering as the felt
experience of thermodynamic entropy, and morality as a thermodynamic
optimization protocol. The Epicurean Paradox is resolved by demonstrating
that its hidden premise---``prevention of all suffering is the highest
good''---is false. Sovereignty (genuine agency) is the higher design
objective.

\medskip

\textbf{Contributions.}
\begin{itemize}
  \item A formal definition of evil as non-terminating recursion, with
    explicit mapping to Turing's Halting Problem.
  \item The suffering decomposition $\mathcal{E} = H + P$ (hardware
    damage + perception error).
  \item The \emph{Fault Isolation Theorem}: any system with autonomous
    agents must implement fault-isolation mechanisms.
  \item A thermodynamic moral vector $\vec{V} = \Delta I / \Delta S$
    that unifies Aristotelian, Kantian, and consequentialist ethics.
  \item A formal resolution of the Epicurean Trilemma via the
    Sovereignty $>$ Safety axiom.
\end{itemize}

\medskip

\textbf{Suggested Reviewers.}
\begin{enumerate}
  \item \textbf{Prof. Alvin Plantinga} (University of Notre Dame) ---
    Author of the Free Will Defense, the most influential modern theodicy.
  \item \textbf{Prof. Robert John Russell} (Graduate Theological Union) ---
    Founder of the Center for Theology and the Natural Sciences.
  \item \textbf{Prof. Nancey Murphy} (Fuller Theological Seminary) ---
    Expert in the philosophy of mind and divine action.
\end{enumerate}

\medskip

This manuscript has not been previously published and is not under consideration
at any other journal. I confirm no conflicts of interest.

\closing{Respectfully submitted,}
\end{letter}
\end{document}
