\documentclass[12pt, a4paper]{letter}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{amssymb}
\usepackage{hyperref}

\geometry{margin=1in}

\hypersetup{colorlinks=true, linkcolor=blue, urlcolor=blue}

\signature{Rafael D. De Paz \\ Independent Researcher \\ \texttt{admin@logos.pub}}
\address{Rafael D. De Paz \\ Independent Researcher \\ \url{https://logos.pub}}

\begin{document}
\begin{letter}{Editorial Board \\ Journal of the ACM \\ Association for Computing Machinery}

\opening{Dear Editors,}

I am writing to submit the enclosed manuscript, entitled

\begin{center}
\textbf{``On the Thermodynamic Separation of P and NP: \\
Computational Irreversibility and the Landauer Barrier,''}
\end{center}

\noindent for consideration for publication in the \textit{Journal of the ACM}.

\medskip

\textbf{Summary.} The paper introduces a physically grounded framework for
separating $\mathsf{P}$ from $\mathsf{NP}$ via Landauer's principle and the
thermodynamic arrow of time. The central contribution is the \emph{Thermodynamic
Church-Turing Thesis} (TCTT)---the axiom that all physical computers obey
Landauer's bound---under which $\mathsf{P} \neq \mathsf{NP}$ follows as a
consequence of the Second Law of Thermodynamics.

\medskip

\textbf{Contributions.} The paper provides:
\begin{itemize}
  \item A formal \emph{thermodynamic complexity measure} $\Theta(f,n)$
    quantifying the irreducible entropy cost of computing $f$.
  \item A proof that one-way functions exhibit a super-polynomial asymmetry
    between evaluation and inversion thermodynamic costs.
  \item A conditional separation $\mathsf{P} \neq \mathsf{NP}$ under the TCTT.
  \item Explicit evasion of all three known barriers: relativization
    (Baker-Gill-Solovay), natural proofs (Razborov-Rudich), and algebrization
    (Aaronson-Wigderson).
\end{itemize}

\medskip

\textbf{Suggested Reviewers.}
\begin{enumerate}
  \item \textbf{Prof. Scott Aaronson} (UT Austin) --- World authority on
    complexity theory and the physics of computation.
  \item \textbf{Prof. Russell Impagliazzo} (UC San Diego) --- Author of the
    ``five worlds'' framework for $\mathsf{P}$ vs $\mathsf{NP}$.
  \item \textbf{Prof. Avi Wigderson} (IAS Princeton) --- Co-author of the
    algebrization barrier and expert in derandomization.
\end{enumerate}

\medskip

This manuscript has not been previously published and is not under consideration
at any other journal. I confirm no conflicts of interest.

\closing{Respectfully submitted,}
\end{letter}
\end{document}
