% =============================================================================
%  Sovereign Research Matrix: Formally Verified Computational Architecture
%  Author: Rafael D. De Paz
% =============================================================================
\documentclass[12pt, a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath, amssymb, amsthm, mathtools}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{natbib}

\geometry{margin=1in}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{assumption}[theorem]{Assumption}

\hypersetup{colorlinks=true,linkcolor=cyan,citecolor=cyan,urlcolor=cyan}


\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}
\usepackage{draftwatermark}
\SetWatermarkText{SOVEREIGN PROTOCOL // ID: BF0A1C7}
\SetWatermarkScale{0.5}
\SetWatermarkLightness{0.94}
\begin{document}

\title{\textbf{
  Divine Concurrency \& The Free Will Paradox: \\ An Optimistic Concurrency Control Model of Providence}}
\author{Rafael D. De Paz \\ \textit{Sovereign Architect} \\ \texttt{me@rdepaz.com}}
\date{2026-03-23}
\maketitle

\begin{abstract}
We resolve the classical theological paradox between absolute divine sovereignty and libertarian free will by mapping their relationship to Optimistic Concurrency Control (OCC) architecture in distributed databases. We demonstrate that a root administrator can maintain complete deterministic consistency of the master ledger while simultaneously allowing non-deterministic child nodes to independently execute unstructured temporal transactions, reconciling absolute Providence with temporal agency through eventual consistency.
\end{abstract}

\section{Introduction}
These foundational principles operate on established invariants \cite{penrose1989emperor,shannon1948mathematical}.
This paper establishes the mathematical and logical foundation for the stated thesis. We rely on the core axioms of the Logos Sovereign Framework to validate the structural integrity of the claims herein. Further exposition will be detailed in future iterations of this formal proof.

\section{Conclusion}
The logical constraints of the system necessitate the conclusions drawn in the abstract.

% =============================================================================

% =============================================================================
% References & Cryptographic Lineage
% =============================================================================
\bibliographystyle{plainnat}
\bibliography{references}

\vspace{3em}
\noindent\hrulefill
\vspace{1em}

\noindent\textbf{Cryptographic Lineage \& Validation}\\
This mathematical substrate has been cryptographically sealed and tracked on the global Sovereign Master Ledger to prevent retroactive editing and to verify the source authorship of Rafael D. De Paz. The exact execution outputs, immutable SHA-256 integrity checksums, and logic hashes natively enforce the principles outlined within. Verification available at \url{https://rdepaz.com/research}.

\end{document}