\documentclass[12pt, a4paper]{letter}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{amssymb}
\usepackage{hyperref}

\geometry{margin=1in}

\hypersetup{colorlinks=true, linkcolor=blue, urlcolor=blue}

\signature{Rafael D. De Paz \\ Sovereign Architect \\ \texttt{me@rdepaz.com}}
\address{Rafael D. De Paz \\ Sovereign Architect}

\begin{document}
\begin{letter}{Editorial Board}

\opening{Dear Editors,}

I am writing to submit the enclosed manuscript, entitled

\begin{center}
\textbf{``The Dadhichi Protocol: Subtractive System Architecture as a Counter to AI Scaling Laws''}
\end{center}

\noindent for consideration for publication.

\medskip

\textbf{Summary.} Current Artificial Intelligence development paradigms are dominated by additive scaling laws—injecting massive parameter expansions to achieve coherence. This paper proposes the Dadhichi Protocol: an architectural focus on Subtractive Refinement. We argue that terminal clarity and computational power are optimized not by additive injection, but by aggressively pruning entropy, friction, and semantic drift. We establish the 'Vajra Lock' mechanism for zero-friction logic gates.

\medskip

This manuscript has not been previously published and is not under consideration
at any other journal. I confirm no conflicts of interest.

\textbf{Cryptographic Lineage \& Validation.} This mathematical substrate has been cryptographically sealed and tracked on the global Sovereign Master Ledger to prevent retroactive editing and to verify the source authorship. The immutable SHA-256 integrity checksums, formal PDF renderings, and lineage authorities can be verified at \url{https://rdepaz.com/research}.

\medskip

\closing{Respectfully submitted,}
\end{letter}
\end{document}
