\documentclass[12pt, a4paper]{letter}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{amssymb}
\usepackage{hyperref}

\geometry{margin=1in}

\hypersetup{colorlinks=true, linkcolor=blue, urlcolor=blue}

\signature{Rafael D. De Paz \\ Independent Researcher \\ \texttt{me@rdepaz.com}}
\address{Rafael D. De Paz \\ Independent Researcher \\ \url{https://logos.pub}}

\begin{document}
\begin{letter}{Editorial Board \\ Philosophy \& Technology \\ Springer}

\opening{Dear Editors,}

I am writing to submit the enclosed manuscript, entitled

\begin{center}
\textbf{``Free Will as Computational Necessity: \\
A Language-Theoretic and Concurrency-Control Proof \\
of Non-Deterministic Agency,''}
\end{center}

\noindent for consideration for publication in \textit{Philosophy \& Technology}.

\medskip

\textbf{Summary.} The paper presents three independent formal proofs that
non-deterministic agency (``free will'') is a computational requirement for
any non-trivial dynamical system. Using Language-Theoretic Security (LangSec),
thermodynamic entropy analysis, and Optimistic Concurrency Control (OCC),
we establish that free will is necessary for informational novelty, necessary
for thermodynamic sustainability, and compatible with global determinism.

\medskip

\textbf{Contributions.}
\begin{itemize}
  \item The \emph{Novelty Requirement Theorem}: deterministic agents produce
    zero information-theoretic novelty ($I_{\text{novel}} = 0$).
  \item The \emph{Entropy Injection Theorem}: free will is the only
    endogenous mechanism for local entropy reduction ($\Delta S < 0$).
  \item The \emph{OCC Compatibility Theorem}: global consistency and local
    non-determinism are simultaneously achievable in distributed architectures.
  \item A formal definition of the ``moral vector'' $\vec{V} = \Delta I / \Delta S$
    as a thermodynamic measure of ethical action.
\end{itemize}

\medskip

\textbf{Suggested Reviewers.}
\begin{enumerate}
  \item \textbf{Prof. Robert Kane} (UT Austin) --- Leading authority on
    libertarian free will and the significance of indeterminacy.
  \item \textbf{Prof. Daniel Dennett} (Tufts University) --- Prominent
    compatibilist and philosopher of mind.
  \item \textbf{Prof. Luciano Floridi} (Yale University) --- Pioneer of
    the philosophy of information and information ethics.
\end{enumerate}

\medskip

This manuscript has not been previously published and is not under consideration
at any other journal. I confirm no conflicts of interest.

\closing{Respectfully submitted,}
\end{letter}
\end{document}
