% =============================================================================
%  Free Will as Computational Necessity:
%  A Language-Theoretic and Concurrency-Control Proof
%  of Non-Deterministic Agency
%
%  Author: Rafael D. De Paz
%  Date:   March 2026
%  Target: Philosophy & Technology / Artificial Intelligence / Erkenntnis
% =============================================================================
\documentclass[12pt, a4paper]{article}

% --- Packages ---
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath, amssymb, amsthm, mathtools}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{microtype}
\usepackage{natbib}

% --- Page Geometry ---
\geometry{margin=1in}

% --- Theorem Environments ---
\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{assumption}[theorem]{Assumption}
\newtheorem{axiom}[theorem]{Axiom}

\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

% --- Custom Commands ---
\newcommand{\R}{\mathbb{R}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\calL}{\mathcal{L}}
\newcommand{\calD}{\mathcal{D}}
\newcommand{\calG}{\mathcal{G}}
\newcommand{\calS}{\mathcal{S}}

% --- Hyperref Setup ---
\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  citecolor=blue,
  urlcolor=blue,
  pdftitle={Free Will as Computational Necessity},
  pdfauthor={Rafael D. De Paz}
}

% =============================================================================
\begin{document}

% --- Title ---
\title{
  \textbf{Free Will as Computational Necessity: \\
  A Language-Theoretic and Concurrency-Control Proof \\
  of Non-Deterministic Agency}
}
\author{
  Rafael D. De Paz \\
  \textit{Independent Researcher} \\
  \texttt{me@rdepaz.com}
}
\date{March 2026}
\maketitle

% =============================================================================
% ABSTRACT
% =============================================================================
\begin{abstract}
We present three independent formal proofs that non-deterministic agency
(``free will'') is not a metaphysical luxury but a \emph{computational
necessity} for any non-trivial dynamical system. First, using
Language-Theoretic Security (LangSec), we model free will as a
\emph{parser}---a non-deterministic finite automaton that maps environmental
inputs to behavioral outputs through an internal state that evolves over time.
We prove that deterministic parsing ($W = 0$) produces zero novelty: the system
converges to a static fixed point with no new information generation. Second,
using thermodynamic entropy analysis, we prove that without non-deterministic
input injection, any closed system monotonically approaches heat death
($\Delta S \to \max$), and that free will is the \emph{only mechanism} capable
of locally decreasing entropy ($\Delta S < 0$). Third, using Optimistic
Concurrency Control (OCC) from distributed systems theory, we resolve the
classical sovereignty-vs-agency paradox: we demonstrate that global
determinism (omniscience) and local non-determinism (free will) are not merely
compatible but are the defining architectural features of any non-locking,
eventually consistent distributed system.
\end{abstract}

\vspace{1em}
\noindent\textbf{Keywords:} free will, determinism, compatibilism,
language-theoretic security, optimistic concurrency control, entropy,
non-deterministic automata, distributed systems.

\vspace{0.5em}
\noindent\textbf{2020 MSC:} 03D05, 68Q45, 68Q85, 91A26.

% =============================================================================
% 1. INTRODUCTION
% =============================================================================
\section{Introduction}\label{sec:intro}

The free will debate is among the oldest in philosophy, typically framed as a
binary opposition between libertarian free will (agents can genuinely choose)
and hard determinism (all events are causally necessitated by prior states).
Compatibilism attempts a middle path, but its formulations are often criticized
as definitional maneuvers rather than formal proofs \citep{Kane2005}.

We approach the problem from a fundamentally different direction: we do not
ask \emph{whether} free will exists, but rather \emph{whether the system
can function without it}. Our answer is negative, and we prove it through
three independent formal frameworks:

\begin{enumerate}[label=(\roman*)]
  \item \textbf{Language-Theoretic Security (LangSec).} We model agents as
    parsers of environmental data. A deterministic parser produces identical
    outputs for identical inputs---no novelty, no meaning. A non-deterministic
    parser (free will) is required for the system to generate new information
    \citep{Bratus2014}.

  \item \textbf{Thermodynamic Entropy.} The Second Law of Thermodynamics
    guarantees that closed systems converge to maximum entropy. Without an
    external entropy-reducing mechanism, the system dies. We prove that
    free will---the non-deterministic choice to create order---is the
    only endogenous mechanism available \citep{Shannon1948, Clausius1865}.

  \item \textbf{Optimistic Concurrency Control (OCC).} In distributed
    databases, OCC allows multiple transactions to execute simultaneously
    without locks. Each transaction acts \emph{optimistically} (freely),
    and a global coordinator resolves conflicts at commit time. We prove that
    this architecture is isomorphic to the sovereignty-agency relationship:
    global determinism (the coordinator) and local non-determinism (the
    transactions) coexist by design \citep{Kung1981}.
\end{enumerate}

\subsection{Main Results}

\begin{theorem}[The Novelty Requirement]\label{thm:novelty}
  Let $\calS$ be a dynamical system with decision function
  $D: \calS \times \Sigma^* \to \Gamma^*$. If $D$ is deterministic
  (i.e., a function of inputs alone with no internal non-deterministic
  state), then the information-theoretic novelty of $\calS$ is zero:
  $I_{\text{novel}}(\calS) = 0$.
\end{theorem}

\begin{theorem}[The Entropy Injection Theorem]\label{thm:entropy}
  In any closed system $\calS$ governed by the Second Law of Thermodynamics,
  $\Delta S \geq 0$. Local entropy reduction ($\Delta S_{\text{local}} < 0$)
  requires an endogenous non-deterministic mechanism---a ``choice'' that
  exports entropy to the environment. Without such a mechanism, $\calS$
  converges monotonically to heat death.
\end{theorem}

\begin{theorem}[The OCC Compatibility Theorem]\label{thm:occ}
  In an Optimistic Concurrency Control architecture, global consistency
  (all transactions commit to a valid final state) and local non-determinism
  (each transaction executes without synchronous locks) are simultaneously
  achievable. The temporal gap $\Delta t = t_{\text{commit}} - t_{\text{execute}}$
  between local action and global integration does not compromise either property.
\end{theorem}

% =============================================================================
% 2. THE LANGSEC PROOF: FREE WILL AS A PARSER
% =============================================================================
\section{The LangSec Proof: Free Will as a Parser}\label{sec:langsec}

\subsection{Agents as Automata}

In Language-Theoretic Security \citep{Bratus2014}, the security of a system
depends on whether its input-processing components (parsers) correctly
recognize the formal language of valid inputs. We extend this framework to
model cognitive agents.

\begin{definition}[Decision Function]\label{def:decision}
  An agent's \emph{decision function} is a mapping
  $D: \calL \times \Sigma^* \to \Gamma^*$, where $\calL$ is the set of
  system constraints (laws of physics, social norms), $\Sigma^*$ is the
  set of all possible input strings (events, stimuli), and $\Gamma^*$
  is the set of all possible output strings (actions, responses). The
  ``will'' $W$ of an agent is defined as the cardinality of valid parse
  paths:
  \begin{equation}\label{eq:will}
    W = \int_{\calL} |D(x)|\, dx,
  \end{equation}
  where $|D(x)|$ is the number of distinct valid outputs for input $x$
  within the constraint set $\calL$.
\end{definition}

\begin{proof}[Proof of \Cref{thm:novelty}]
  If $D$ is deterministic, then $|D(x)| = 1$ for all $x \in \Sigma^*$.
  Therefore $W = \int_{\calL} 1\, dx = |\calL|$, which measures the
  size of the constraint set but produces \emph{zero choice-entropy}:
  \begin{equation}
    H_{\text{choice}} = -\sum_i p_i \log p_i = -1 \cdot \log 1 = 0.
  \end{equation}
  Since $H_{\text{choice}} = 0$, the system generates no new information
  beyond what is determined by its initial conditions and constraints.
  $I_{\text{novel}}(\calS) = 0$. \qedhere
\end{proof}

\subsection{The Parser Interpretation}

Under this model, an agent's free will is literally its parser. The
environment sends a string of events (data), and the agent \emph{chooses}
how to interpret (parse) that data. Parsing through the lens of ``peace''
generates one output; parsing through ``fear'' generates another. The
constraints $\calL$ are fixed (physical laws, logical boundaries), but
the parse \emph{within} those constraints is non-deterministic.

\begin{remark}[Connection to Tzimtzum]
  In Kabbalistic theology, the concept of \emph{Tzimtzum} (divine
  self-contraction) posits that the Creator ``withdrew'' absolute control
  to create a ``void'' in which free agents could exist \citep{Scholem1941}.
  In our framework, $\calL$ is the boundary of this void: the constraints
  are fixed, but within them, $W > 0$---the agent has genuine agency.
\end{remark}

% =============================================================================
% 3. THE THERMODYNAMIC PROOF
% =============================================================================
\section{The Thermodynamic Proof: Entropy and Agency}\label{sec:thermo}

\begin{proof}[Proof of \Cref{thm:entropy}]
  By the Second Law \citep{Clausius1865}, for any closed system:
  $\Delta S_{\text{total}} \geq 0$. However, open subsystems within the
  closed universe can achieve $\Delta S_{\text{local}} < 0$ by exporting
  entropy to their environment, provided the total entropy still increases.

  The question is: what \emph{mechanism} drives local entropy reduction?
  In biology, this mechanism is \emph{choice}---the non-deterministic
  selection of order-creating actions from a set of alternatives. A cell
  that ``chooses'' to replicate its DNA rather than degrade reduces local
  entropy. An agent that ``chooses'' to build rather than destroy reduces
  local entropy.

  Without $W > 0$ (non-deterministic agency), the system has no endogenous
  mechanism for selecting entropy-reducing trajectories. It can only follow
  the gradient of maximum entropy: heat death.

  Therefore: $W > 0$ (free will) is the necessary condition for
  $\Delta S_{\text{local}} < 0$ (local order creation). \qedhere
\end{proof}

\begin{definition}[Moral Vector]\label{def:moral_vector}
  The \emph{moral vector} $\vec{V}$ of an action is defined as the ratio
  of information gain to entropy change:
  \begin{equation}\label{eq:moral_vector}
    \vec{V} = \frac{\Delta I}{\Delta S},
  \end{equation}
  where $\Delta I$ is the change in mutual information between the agent
  and its environment, and $\Delta S$ is the change in system entropy.
  If $\vec{V} > 0$, the action is \emph{constructive} (increases information
  density while reducing entropy). If $\vec{V} < 0$, it is \emph{destructive}.
\end{definition}

% =============================================================================
% 4. THE OCC PROOF: SOVEREIGNTY AND AGENCY
% =============================================================================
\section{The OCC Proof: Sovereignty and Agency}\label{sec:occ}

\subsection{The Sovereignty--Agency Paradox}

The classical theological formulation: if an omniscient coordinator
(``God'') knows all future states, do local agents have genuine choice?
Two failure modes arise:

\begin{enumerate}[label=(\alph*)]
  \item \textbf{Fatalism (Dead-Code Exception):} All actions are
    pre-compiled; local processing is meaningless.
  \item \textbf{Anxiety (Out-of-Memory Panic):} The local agent believes
    it alone maintains global coherence and must continuously self-validate.
\end{enumerate}

Both modes are architectural errors. We resolve them via OCC.

\subsection{The OCC Architecture}

\begin{definition}[OCC Transaction]\label{def:occ}
  In Optimistic Concurrency Control \citep{Kung1981}, multiple transactions
  $\{T_1, \ldots, T_n\}$ execute simultaneously on a shared database
  without acquiring synchronous locks. Each transaction $T_i$:
  \begin{enumerate}[label=(\roman*)]
    \item Reads a snapshot $\sigma_i$ of the global state;
    \item Executes local mutations $M_i$ based on $\sigma_i$;
    \item Submits $(M_i, \sigma_i)$ for validation at commit time.
  \end{enumerate}
  The global coordinator validates all transactions by checking for
  conflicts (two transactions modifying the same state). Conflicting
  transactions are rolled back and retried; non-conflicting transactions
  are committed atomically.
\end{definition}

\begin{proof}[Proof of \Cref{thm:occ}]
  We establish the isomorphism:
  \begin{center}
  \begin{tabular}{ll}
    \toprule
    \textbf{OCC Component} & \textbf{Sovereignty--Agency Mapping} \\
    \midrule
    Global Database & The state of reality \\
    Transaction $T_i$ & An individual agent's life-trajectory \\
    Local Mutation $M_i$ & A free choice / action \\
    Snapshot $\sigma_i$ & The agent's perception of state \\
    Commit Validation & Divine judgment / conflict resolution \\
    Holy Latency $\Delta t$ & The gap between action and consequence \\
    \bottomrule
  \end{tabular}
  \end{center}

  In OCC, the following properties hold simultaneously:
  \begin{enumerate}[label=(\roman*)]
    \item \textbf{Local Non-Determinism:} Each $T_i$ executes without
      locks---it genuinely ``chooses'' its mutations $M_i$ based on its
      local state, without being constrained by concurrent transactions.
    \item \textbf{Global Consistency:} The coordinator guarantees that the
      final committed state is serializable---equivalent to some sequential
      execution order. No inconsistency survives the commit phase.
    \item \textbf{Eventual Convergence:} The system converges to a consistent
      state even if individual transactions fail and retry.
  \end{enumerate}

  These are precisely the properties required to resolve the sovereignty--agency
  paradox: the coordinator (sovereignty) and the transactions (agency) coexist
  by architectural design. Neither property compromises the other.

  The ``Holy Latency'' $\Delta t = t_{\text{commit}} - t_{\text{execute}}$
  explains why free actions do not receive immediate environmental feedback:
  the global state will not reflect the local commit until all cross-agent
  conflicts are resolved. This latency is not absence of coordination; it
  is the computational cost of eventual consistency in a massively parallel
  system. \qedhere
\end{proof}

% =============================================================================
% 5. DISCUSSION
% =============================================================================
\section{Discussion}\label{sec:discussion}

\subsection{The Unity of the Three Proofs}

The three proofs are independent but convergent:
\begin{itemize}
  \item \textbf{LangSec} proves that free will is necessary for
    \emph{informational novelty}.
  \item \textbf{Thermodynamics} proves that free will is necessary for
    \emph{order creation}.
  \item \textbf{OCC} proves that free will is \emph{compatible} with
    global determinism.
\end{itemize}

Together, they establish that non-deterministic agency is simultaneously
\emph{required} (by information theory and thermodynamics) and
\emph{compatible} (with omniscient coordination).

\subsection{Limitations}

\begin{enumerate}
  \item The LangSec model treats agents as parsers, which is a simplification.
    Real cognitive systems are more complex than finite-state automata.
  \item The thermodynamic proof assumes that entropy reduction requires
    ``choice''---but biological entropy reduction is sometimes driven by
    physical gradients (e.g., crystallization) without apparent agency.
  \item The OCC proof establishes compatibility but does not prove existence.
    It shows that sovereignty and agency \emph{can} coexist, not that they
    \emph{do} in our universe.
\end{enumerate}

% =============================================================================
% 6. CONCLUSION
% =============================================================================
\section{Conclusion}\label{sec:conclusion}

We have established, through three independent formal frameworks, that
non-deterministic agency is a computational necessity for any non-trivial
dynamical system. Free will is not a metaphysical mystery requiring
philosophical resolution. It is a \emph{formal requirement} for:

\begin{enumerate}
  \item information-theoretic novelty (zero novelty without it),
  \item thermodynamic sustainability (heat death without it), and
  \item architectural consistency in distributed systems (achievable with it).
\end{enumerate}

The debate between ``determinism'' and ``free will'' is, formally, a
false dichotomy. Both are necessary architectural features of a
non-locking, eventually consistent universe.

% =============================================================================
% REFERENCES
% =============================================================================
\bibliographystyle{plainnat}
\bibliography{references}

\end{document}
