\documentclass[12pt, a4paper]{letter}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{amssymb}
\usepackage{hyperref}

\geometry{margin=1in}

\hypersetup{colorlinks=true, linkcolor=blue, urlcolor=blue}

\signature{Rafael D. De Paz \\ Independent Researcher \\ \texttt{me@rdepaz.com}}
\address{Rafael D. De Paz \\ Independent Researcher}

\begin{document}
\begin{letter}{Editorial Board}

\opening{Dear Editors,}

I am writing to submit the enclosed manuscript, entitled

\begin{center}
\textbf{``The Simulation Hypothesis Audit: \\ G\"odel, the Turing Limit, and the Necessity of a Non-Algorithmic Root''}
\end{center}

\noindent for consideration for publication.

\medskip

\textbf{Summary.} We apply G\"odel's First Incompleteness Theorem and the Turing Halting Problem directly to Nick Bostrom's Simulation Hypothesis. We formally prove that any simulated universe running on a Turing-complete substrate must necessarily contain localized undecidable propositions that induce system-wide stack overflows unless structurally supported by a Non-Algorithmic Origin fundamentally outside the computational boundary. Consequently, a purely algorithmic, infinite regress 'ancestor simulation' is mathematically impossible.

\medskip

This manuscript has not been previously published and is not under consideration
at any other journal. I confirm no conflicts of interest.

\textbf{Cryptographic Lineage \& Validation.} This mathematical substrate has been cryptographically sealed and tracked on the global Sovereign Master Ledger to prevent retroactive editing and to verify the source authorship. The immutable SHA-256 integrity checksums, formal PDF renderings, and lineage authorities can be verified at \url{https://rdepaz.com/research}.

\medskip

\closing{Respectfully submitted,}
\end{letter}
\end{document}
