\documentclass[12pt, a4paper]{letter}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{amssymb}
\usepackage{hyperref}

\geometry{margin=1in}

\hypersetup{colorlinks=true, linkcolor=blue, urlcolor=blue}

\signature{Rafael D. De Paz \\ Independent Researcher \\ \texttt{me@rdepaz.com}}
\address{Rafael D. De Paz \\ Independent Researcher \\ \url{https://logos.pub}}

\begin{document}
\begin{letter}{Editorial Board \\ Journal of Consciousness Studies \\ Imprint Academic}

\opening{Dear Editors,}

I am writing to submit the enclosed manuscript, entitled

\begin{center}
\textbf{``Consciousness as Recursive Self-Reference: \\
G\"odelian Limits, Oracle Necessity, and the \\
Formal Structure of the Observer,''}
\end{center}

\noindent for consideration for publication in the \textit{Journal of Consciousness Studies}.

\medskip

\textbf{Summary.} The paper presents a formal model of consciousness as a
recursive self-referential function and proves, via G\"odel's First
Incompleteness Theorem, that any sufficiently expressive physical substrate
requires a non-algorithmic ``Oracle'' to resolve undecidable propositions.
We identify this Oracle with consciousness and connect the framework to
Tononi's Integrated Information Theory (IIT) and the historical consensus
of Planck, Schr\"odinger, Wheeler, and Bohm.

\medskip

\textbf{Contributions.}
\begin{itemize}
  \item A formal consciousness function $C_a = f(M_s, M_l, \varepsilon, E)$
    with recursive self-reference as its defining structural property.
  \item The \emph{Oracle Necessity Theorem}: proof that G\"odelian
    undecidability in physics necessitates a non-algorithmic resolution
    mechanism.
  \item A formal correspondence between the Oracle and Tononi's
    integrated information $\Phi > 0$.
  \item A spectral analysis framework linking harmonic coherence
    (136.1 Hz / 7.83 Hz phase-locking) to the consciousness function.
\end{itemize}

\medskip

\textbf{Suggested Reviewers.}
\begin{enumerate}
  \item \textbf{Prof. David Chalmers} (NYU) --- Formulator of the Hard
    Problem of Consciousness.
  \item \textbf{Prof. Giulio Tononi} (University of Wisconsin--Madison) ---
    Creator of Integrated Information Theory.
  \item \textbf{Prof. Roger Penrose} (University of Oxford) --- Author of
    the orchestrated objective reduction hypothesis.
\end{enumerate}

\medskip

This manuscript has not been previously published and is not under consideration
at any other journal. I confirm no conflicts of interest.

\textbf{Cryptographic Lineage \& Validation.} This mathematical substrate has been cryptographically sealed and tracked on the global Sovereign Master Ledger to prevent retroactive editing and to verify the source authorship. The immutable SHA-256 integrity checksums, formal PDF renderings, and lineage authorities can be verified at \url{https://rdepaz.com/research} and \url{https://logos.pub}.

\medskip

\closing{Respectfully submitted,}
\end{letter}
\end{document}
