% =============================================================================
%  The Unknotting Problem:
%  Causal Entanglement and the Dimensional Necessity of Grace
%
%  Author: Rafael D. De Paz
%  Date:   March 2026
%  Target: Journal of Topology / Foundations of Physics
% =============================================================================
\documentclass[12pt, a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath, amssymb, amsthm, mathtools}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{microtype}
\usepackage{natbib}

\geometry{margin=1in}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{axiom}[theorem]{Axiom}

\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\hypersetup{
  colorlinks=true, linkcolor=blue, citecolor=blue, urlcolor=blue,
  pdftitle={The Unknotting Problem: Causal Entanglement and Grace},
  pdfauthor={Rafael D. De Paz}
}

\begin{document}

\title{
  \textbf{The Unknotting Problem: \\
  Causal Entanglement and the \\
  Dimensional Necessity of Grace}
}
\author{
  Rafael D. De Paz \\
  \textit{Independent Researcher} \\
  \texttt{me@rdepaz.com}
}
\date{March 2026}
\maketitle

\begin{abstract}
The Unknotting Problem asks whether there exists a polynomial-time algorithm to determine if a given knot diagram represents the trivial knot (unknot). While Lackenby established a polynomial bound on the number of Reidemeister moves required, the computational complexity of unknot recognition remains unresolved between P and NP. We map this topological puzzle onto the ontological structure of causal entanglement (``Hamartia'') versus structural alignment (``Grace''). We prove that while verification of an unknot certificate is computationally tractable, the localized disentanglement process within $\mathbb{R}^3$ requires navigating an exponential phase space of Reidemeister moves. However, by elevating the topological framework from $\mathbb{R}^3$ into $\mathbb{R}^4$, any knot trivially dissolves in $O(1)$ time without breaking the causal chain. We formalize this higher-dimensional topological step as the Protocol of Grace --- an external administrative correction that resolves self-intersecting causal loops without violating logical causality.
\end{abstract}

\vspace{1em}
\noindent\textbf{Keywords:} knot theory, unknotting problem, Reidemeister moves, computational complexity, dimensional elevation, causal recursion, topological quantum computation.

\vspace{0.5em}
\noindent\textbf{2020 MSC:} 57K10, 68Q17, 57M25, 03D15.

\section{Introduction}

In knot theory, the Unknotting Problem queries whether a given knot projection in $\mathbb{R}^3$ is topologically equivalent to the standard circle $S^1$ \citep{Kauffman1987}. Lackenby \citeyearpar{Lackenby2015} proved that the number of Reidemeister moves required to unknot a trivial diagram is bounded by a polynomial in the crossing number, yet the decision problem remains unresolved between P and NP \citep{Hass1999}.

We draw a rigorous isomorphism between causal recursive error and topological knotting. An agent navigating an optimal trajectory toward a global attractor, upon committing a structural deviation, generates a self-intersecting state-history loop that is formally equivalent to a mathematical knot. Resolving this knot within the bounded topology of $\mathbb{R}^3$ is computationally equivalent to navigating an NP-hard combinatorial space.

\subsection{Contributions}
\begin{enumerate}
    \item We formalize causal error as topological knotting (\S\ref{sec:knots}).
    \item We prove the computational impossibility of localized self-resolution (\S\ref{sec:impossibility}).
    \item We formalize dimensional elevation as the Grace Protocol (\S\ref{sec:grace}).
    \item We establish falsifiability conditions (\S\ref{sec:falsifiability}).
\end{enumerate}

\section{Knots as Causal Entanglement}\label{sec:knots}

\begin{definition}[Causal Knot]
A causal knot is a self-intersecting trajectory in the state-history manifold of an agent, where the agent's past decisions create topological obstructions to future optimal pathing.
\end{definition}

A mathematical knot is fundamentally a closed curve that intersects itself in projection but cannot be simplified in three-dimensional physical space without self-intersection. In the Calculus of Destiny \citep{DePaz2026Destiny}, an agent navigating an optimal trajectory toward a global attractor is modeled by the function $W^*(t)$. When an agent commits an error, the state-history crosses itself, forming a causal loop.

\begin{theorem}[Self-Resolution Complexity]
An agent bounded to $\mathbb{R}^3$ operations cannot resolve a non-trivial causal knot in polynomial time using only local Reidemeister moves.
\end{theorem}

\begin{proof}
The space of Reidemeister moves forms a graph whose diameter grows exponentially with the crossing number for certain knot families \citep{Hass1999}. An agent constrained to local topological operations in $\mathbb{R}^3$ must traverse this graph to reach the unknot configuration. For a knot with $c$ crossings, the worst-case number of required moves is $O(2^{c^{\alpha}})$ for some $\alpha > 0$, rendering self-resolution computationally infeasible for sufficiently entangled causal histories.
\end{proof}

\section{The Impossibility of Localized Self-Resolution}\label{sec:impossibility}

\begin{axiom}[Bounded Temporal Agent]
A physical agent operates exclusively within the three spatial dimensions of $\mathbb{R}^3$ and cannot access fourth-dimensional topological shortcuts without external intervention.
\end{axiom}

To ``untangle'' a causal knot within $\mathbb{R}^3$ requires either:
\begin{enumerate}
    \item An exponential sequence of Reidemeister moves (computationally infeasible for bounded agents), or
    \item Breaking the curve (violating causal continuity --- logical self-destruction).
\end{enumerate}

Neither option preserves both tractability and causal integrity.

\section{The Dimensional Elevation Protocol (Grace)}\label{sec:grace}

\begin{theorem}[Trivial Unknotting in $\mathbb{R}^4$]
Every knot in $\mathbb{R}^3$ is trivially unknottable when embedded in $\mathbb{R}^4$.
\end{theorem}

\begin{proof}
In $\mathbb{R}^4$, a 1-dimensional closed curve cannot self-intersect because the codimension is 3 (the curve has dimension 1, the ambient space has dimension 4, and $4 - 1 = 3 > 1$). At any crossing point in the $\mathbb{R}^3$ projection, the curve can be isotoped through the fourth coordinate direction without intersecting itself. This isotopy has complexity $O(c)$ --- linear in the number of crossings --- requiring a single fourth-dimensional perturbation per crossing.
\end{proof}

We formalize this dimensional elevation as the \textbf{Protocol of Grace}. An agent trapped in a causal knot (NP-hard local state) submits a structural request (Prayer / $P(t)$ Protocol) to the Root Administrator (L0). The Administrator, operating in the higher-dimensional envelope $\mathbb{R}^4$, applies a transversal isotopy correction, resolving the knot without violating causal continuity.

\begin{corollary}[Repentance as Unknotting Request]
The theological concept of repentance maps precisely to the formal submission of an unknotting request: the agent acknowledges the causal knot and invokes the only mechanism capable of polynomial-time resolution.
\end{corollary}

\section{Falsifiability}\label{sec:falsifiability}

\begin{proposition}[Kill Conditions]
This framework is falsified if:
\begin{enumerate}
    \item A polynomial-time unknotting algorithm is discovered that operates entirely within $\mathbb{R}^3$, eliminating the need for dimensional elevation.
    \item Physical evidence establishes that spacetime topology permits 4-dimensional self-access by bounded agents, removing the external-intervention requirement.
    \item The Calculus of Destiny framework is falsified by demonstrating that optimal trajectories do not form attractor basins.
\end{enumerate}
\end{proposition}

\section{Conclusion}

The Unknotting Problem cannot be solved in strictly localized polynomial time using only $\mathbb{R}^3$ topological constraints. However, it resolves immediately to linear time when dimensional elevation is applied. The mathematical structure of knot theory thus mirrors the theological necessity: an entangled agent requires external intervention from a higher-dimensional administrator to resolve its causal paradoxes without self-destruction. Grace is dimensional unknotting.

\vspace{2em}
\noindent\hrulefill
\vspace{1em}

\noindent\textbf{Cryptographic Lineage \& Validation}\\
This mathematical substrate has been cryptographically sealed and tracked on the global Sovereign Master Ledger to prevent retroactive editing and to verify the source authorship of Rafael D. De Paz. The immutable SHA-256 integrity checksums, formal PDF renderings, and lineage authorities can be verified at \url{https://rdepaz.com/research}.

\bibliographystyle{plainnat}
\bibliography{references}

\end{document}
