\documentclass[12pt, a4paper]{letter}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{amssymb}
\usepackage{hyperref}

\geometry{margin=1in}

\hypersetup{colorlinks=true, linkcolor=blue, urlcolor=blue}

\signature{Rafael D. De Paz \\ Sovereign Architect \\ \texttt{me@rdepaz.com}}
\address{Rafael D. De Paz \\ Sovereign Architect}

\begin{document}
\begin{letter}{Editorial Board}

\opening{Dear Editors,}

I am writing to submit the enclosed manuscript, entitled

\begin{center}
\textbf{``Sliding-Window MTD Caching: Achieving $O(1)$ Verification Speed in Stateful Systems''}
\end{center}

\noindent for consideration for publication.

\medskip

\textbf{Summary.} Moving Target Defense (MTD) is recognized as a robust network security paradigm. This paper details the mathematical profiling of an MTD synchronized with a Sliding-Window Schema Cache. By storing validation states precisely aligned with the MTD rotation phase, an ALSF (Adaptive Linguistic Security Framework) gateway can reduce ingestion validation from $O(N)$ linear time ($\approx 1.19$ms) to $O(1)$ constant time ($\approx 0.00004$ms) on repeating payloads, achieving a 30,000x acceleration without compromising dynamic cryptographic integrity.

\medskip

This manuscript has not been previously published and is not under consideration
at any other journal. I confirm no conflicts of interest.

\textbf{Cryptographic Lineage \& Validation.} This mathematical substrate has been cryptographically sealed and tracked on the global Sovereign Master Ledger to prevent retroactive editing and to verify the source authorship. The immutable SHA-256 integrity checksums, formal PDF renderings, and lineage authorities can be verified at \url{https://rdepaz.com/research}.

\medskip

\closing{Respectfully submitted,}
\end{letter}
\end{document}
