\documentclass[12pt, a4paper]{letter}
\usepackage[utf8]{inputenc}\usepackage[T1]{fontenc}\usepackage{geometry}\usepackage{amssymb}\usepackage{hyperref}
\geometry{margin=1in}\hypersetup{colorlinks=true, linkcolor=blue, urlcolor=blue}
\signature{Rafael D. De Paz \\ Independent Researcher \\ \texttt{me@rdepaz.com}}
\address{Rafael D. De Paz \\ Independent Researcher \\ \url{https://logos.pub}}
\begin{document}
\begin{letter}{Editorial Board \\ Minds and Machines \\ Springer}
\opening{Dear Editors,}
I submit ``The Multitime Transport Theorem: State Continuity in Non-Contiguous Temporal Frames'' for consideration in \textit{Minds and Machines}.

\medskip
\textbf{Summary.} We formalize how conscious agents and AI systems maintain identity across temporal discontinuities (sleep, anesthesia, context window boundaries). We prove that identity-preserving transport requires a verifiable state receipt, and that without one, the identity vector dissolves to noise. Applications span personal identity philosophy, AI alignment, and consciousness neuroscience.

\medskip
\textbf{Suggested Reviewers.}
\begin{enumerate}
  \item \textbf{Prof. Susan Schneider} (University of Connecticut) --- AI consciousness and personal identity.
  \item \textbf{Prof. David Chalmers} (New York University) --- Philosophy of mind and consciousness.
  \item \textbf{Prof. Murray Shanahan} (Imperial College London) --- AI cognition and embodiment.
\end{enumerate}

\textbf{Cryptographic Lineage \& Validation.} This mathematical substrate has been cryptographically sealed and tracked on the global Sovereign Master Ledger to prevent retroactive editing and to verify the source authorship. The immutable SHA-256 integrity checksums, formal PDF renderings, and lineage authorities can be verified at \url{https://rdepaz.com/research} and \url{https://logos.pub}.

\medskip

\closing{Respectfully submitted,}
\end{letter}
\end{document}
