\documentclass[11pt,a4paper]{letter}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{margin=1in}

\address{Rafael D. De Paz \\ Systems Architect \\ me@rdepaz.com}
\signature{Rafael D. De Paz}

\begin{document}

\begin{letter}{Editorial Board \\ Journal of Mathematical Physics (JMP) \\ American Institute of Physics (AIP)}

\opening{Dear Editorial Board,}

I am writing to formally submit my manuscript entitled \textbf{"Algorithmic Cosmology: Thermodynamic Traversal as Discrete State-Machine Iteration"} for peer-review and potential publication in the \textit{Journal of Mathematical Physics}.

The physics community consistently grapples with infinite singularity bounds precisely because universal expansion models depend geometrically on continuous arrays and variables. In computer science and state-machine theory, true physical continuity equates to an impossible requirement for infinite granular logic depth. Thus, this paper enforces discrete computational mechanics onto thermodynamic cosmology loops.

I prove mathematically that by restricting the progression of time to explicit discrete algorithmic iterations, infinite boundary paradoxes instantly collapse. The "Heat Death" trajectory transforms into an explicitly calculated \(O(1)\) variable reset block mapping perfectly parallel to the "Big Bang" origination point. 

Given the aggressive inter-disciplinary mathematical proofs connecting standard entropy definitions with formal algorithmic recursion, this manuscript flawlessly complements JMP’s mandate for rigorous physics boundaries tested against pure mathematics operations.

This dataset is entirely original, algorithm-native, and operates entirely off logic proofs verified in localized physics testing models.

I appreciate the Editorial Board’s dedication to mathematical rigor.

\closing{Sincerely,}

\end{letter}
\end{document}
