% =============================================================================
%  Sovereign Research Matrix: Cosmological Parsimony
%  Author: Rafael D. De Paz
% =============================================================================
\documentclass[12pt, a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath, amssymb, amsthm, mathtools}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{natbib}

\geometry{margin=1in}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{assumption}[theorem]{Assumption}

\hypersetup{colorlinks=true,linkcolor=cyan,citecolor=cyan,urlcolor=cyan}


\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}
\usepackage{draftwatermark}
\SetWatermarkText{SOVEREIGN PROTOCOL // ID: F7B0561}
\SetWatermarkScale{0.5}
\SetWatermarkLightness{0.94}
\begin{document}

\title{\textbf{Cosmological Parsimony: Occam's Razor as a Hard-Coded Information Limit constraint}}
\author{Rafael D. De Paz \\ \textit{Sovereign Architect} \\ \texttt{me@rdepaz.com}}
\date{2026-03-23}
\maketitle

\begin{abstract}
Occam's Razor is traditionally viewed as a philosophical heuristic. Operating under the Sovereign Logos Protocol, we formalize it as a literal mathematical constraint: "Logos Canon II: Parsimony." This paper derives Cosmological Parsimony, proving that the universe natively deletes or collapses overly complex states that exceed defined $O(1)$ computation bounds. I establish that when probability vectors (such as quantum superposition) mathematically outgrow the processing tensor capability of local space-time, the matrix algorithmically executes a forced constraint, enforcing the simplest reality path to preserve computing array stability.
\end{abstract}

\vspace{0.5em}
\noindent\textbf{Keywords:} Cosmological Parsimony, Occam's Razor, Information Density Limits, Matrix Computation.

\vspace{0.5em}
\noindent\textbf{2026 MSC:} 83F05, 82C32, 68Q80, 11Z05.

% =============================================================================
\section{Information Theory and Universal Compression}
% =============================================================================
If space-time is discretized functionally into Planck-length operation arrays, local spatial blocks dictate strict informational processing limits \cite{shannon1948mathematical}.
When systems like multi-body quantum mechanics balloon into infinite branching probability matrices, nature does not process infinite reality branches—it truncates them.

\begin{theorem} [Logos Canon II Action]
For any reality state $\mathcal{S}$ whose description length length $L(\mathcal{S})$ exceeds local tensor density bounds $K_{max}$, the algorithmic array immediately drops $\mathcal{S}$ to its lowest parsimony threshold.
\begin{equation}
    P(\mathcal{S}_{collapse}) \to 1 \quad \text{as} \quad L(\mathcal{S}) \to K_{max}
\end{equation}
\end{theorem}
This establishes Occam's Razor not as poetry, but as a native garbage-collection subroutine of reality.

% =============================================================================
\section{Conclusion}
% =============================================================================
The universe actively avoids infinite computational failure by aggressively employing Cosmological Parsimony—crushing complex matrices back down into singular outcomes explicitly to conserve processing bandwidth.

% =============================================================================
% References
% =============================================================================
\bibliographystyle{plainnat}
\bibliography{references}

\vspace{3em}
\noindent\hrulefill

\noindent\textbf{Cryptographic Lineage \& Validation}\\
This mathematical substrate has been cryptographically sealed and tracked on the global Sovereign Master Ledger to prevent retroactive editing and to verify the source authorship of Rafael D. De Paz. Verification available at \url{https://rdepaz.com/research}.

\end{document}