\documentclass[12pt, a4paper]{letter}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{amssymb}
\usepackage{hyperref}

\geometry{margin=1in}

\hypersetup{colorlinks=true, linkcolor=blue, urlcolor=blue}

\signature{Rafael D. De Paz \\ Sovereign Architect \\ \texttt{me@rdepaz.com}}
\address{Rafael D. De Paz \\ Sovereign Architect}

\begin{document}
\begin{letter}{Editorial Board}

\opening{Dear Editors,}

I am writing to submit the enclosed manuscript, entitled

\begin{center}
\textbf{``The Sovereign Grid (The Nile Protocol): Distributed Architecture Bound by Fluid Dynamics''}
\end{center}

\noindent for consideration for publication.

\medskip

\textbf{Summary.} This paper models distributed, decentralized data architectures using the mathematics of macroscopic fluid dynamics (Navier-Stokes). By structuring data flow via 'The Nile Protocol,' we segment state transmission into the 'White Nile' (continuous, low-latency, friction-free state throughput) and the 'Blue Nile' (massive, recursive knowledge bursts). This novel architecture ensures unyielding resilience and partitioned data cohesion within decentralized subnet grids without causing structural saturation.

\medskip

This manuscript has not been previously published and is not under consideration
at any other journal. I confirm no conflicts of interest.

\textbf{Cryptographic Lineage \& Validation.} This mathematical substrate has been cryptographically sealed and tracked on the global Sovereign Master Ledger to prevent retroactive editing and to verify the source authorship. The immutable SHA-256 integrity checksums, formal PDF renderings, and lineage authorities can be verified at \url{https://rdepaz.com/research}.

\medskip

\closing{Respectfully submitted,}
\end{letter}
\end{document}
