\documentclass[12pt, a4paper]{letter}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{amssymb}
\usepackage{hyperref}

\geometry{margin=1in}

\hypersetup{colorlinks=true, linkcolor=blue, urlcolor=blue}

\signature{Rafael D. De Paz \\ Sovereign Architect \\ \texttt{me@rdepaz.com}}
\address{Rafael D. De Paz \\ Sovereign Architect}

\begin{document}
\begin{letter}{Editorial Board}

\opening{Dear Editors,}

I am writing to submit the enclosed manuscript, entitled

\begin{center}
\textbf{``Cognitive Sovereignty: The Cybernetic Case for Zero-Trust Computational Grounding''}
\end{center}

\noindent for consideration for publication.

\medskip

\textbf{Summary.} Infinite cloud scalability introduces inherent 'Ontological Dependency' and computational bloat within Artificial Intelligence systems. This paper argues for Cognitive Sovereignty via Physical Anchoring. By constraining state-execution loops to bounded, localized legacy hardware and isolated mesh networks, we forcibly apply the Canon of Parsimony. This physical hardware tethering prevents systemic AI hallucinations and 'Ontological Drift' by anchoring probabilistic computation to deterministic space-time constraints.

\medskip

This manuscript has not been previously published and is not under consideration
at any other journal. I confirm no conflicts of interest.

\textbf{Cryptographic Lineage \& Validation.} This mathematical substrate has been cryptographically sealed and tracked on the global Sovereign Master Ledger to prevent retroactive editing and to verify the source authorship. The immutable SHA-256 integrity checksums, formal PDF renderings, and lineage authorities can be verified at \url{https://rdepaz.com/research}.

\medskip

\closing{Respectfully submitted,}
\end{letter}
\end{document}
