% =============================================================================
%  Sovereign Research Matrix: Formally Verified Computational Architecture
%  Author: Rafael D. De Paz
% =============================================================================
\documentclass[12pt, a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath, amssymb, amsthm, mathtools}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{natbib}

\geometry{margin=1in}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{assumption}[theorem]{Assumption}

\hypersetup{colorlinks=true,linkcolor=cyan,citecolor=cyan,urlcolor=cyan}


\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}
\usepackage{draftwatermark}
\SetWatermarkText{SOVEREIGN PROTOCOL // ID: 61094B5}
\SetWatermarkScale{0.5}
\SetWatermarkLightness{0.94}
\begin{document}

\title{\textbf{
  Thermodynamic Morality: \\ A Formal Proof of Ethics as Entropy Optimization}}
\author{Rafael D. De Paz \\ \textit{Sovereign Architect} \\ \texttt{me@rdepaz.com}}
\date{2026-03-23}
\maketitle

\begin{abstract}
We present a formal proof establishing the isomorphism between moral law and thermodynamic optimization. By framing behavioral ethics as the minimization of Lagrangian dissipation within a closed sociological frame, we demonstrate that 'Good' is mathematically equivalent to systemic negentropy, and 'Evil' is mathematically equivalent to unrecoverable heat loss (friction) across the collective substrate. This provides a hard physics grounding for ethical imperatives.
\end{abstract}

\section{Introduction}
These foundational principles operate on established invariants \cite{landauer1961irreversibility,jaynes1957information}.
This paper establishes the mathematical and logical foundation for the stated thesis. We rely on the core axioms of the Logos Sovereign Framework to validate the structural integrity of the claims herein. Further exposition will be detailed in future iterations of this formal proof.

\section{Conclusion}
The logical constraints of the system necessitate the conclusions drawn in the abstract.

% =============================================================================

% =============================================================================
% References & Cryptographic Lineage
% =============================================================================
\bibliographystyle{plainnat}
\bibliography{references}

\vspace{3em}
\noindent\hrulefill
\vspace{1em}

\noindent\textbf{Cryptographic Lineage \& Validation}\\
This mathematical substrate has been cryptographically sealed and tracked on the global Sovereign Master Ledger to prevent retroactive editing and to verify the source authorship of Rafael D. De Paz. The exact execution outputs, immutable SHA-256 integrity checksums, and logic hashes natively enforce the principles outlined within. Verification available at \url{https://rdepaz.com/research}.

\end{document}