\documentclass[12pt, a4paper]{letter}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{amssymb}
\usepackage{hyperref}

\geometry{margin=1in}

\hypersetup{colorlinks=true, linkcolor=blue, urlcolor=blue}

\signature{Rafael D. De Paz \\ Sovereign Architect \\ \texttt{me@rdepaz.com}}
\address{Rafael D. De Paz \\ Sovereign Architect}

\begin{document}
\begin{letter}{Editorial Board}

\opening{Dear Editors,}

I am writing to submit the enclosed manuscript, entitled

\begin{center}
\textbf{``The Lineage Algorithm: Biological Generations as Computational Boot Sequences''}
\end{center}

\noindent for consideration for publication.

\medskip

\textbf{Summary.} We establish an isomorphism between biological generational transmission and software engineering load sequences. We model the Ancestral layer as the immutable BIOS establishing non-volatile security perimeters, the Parental layer as the OS kernel providing environmental transmission rules, and the Individual layer as the mutable Userland Application executing the payload. We mathematically evaluate structural invariance across inherited substrates, positing that systemic sociological stability fundamentally relies on unchanged core firmware.

\medskip

This manuscript has not been previously published and is not under consideration
at any other journal. I confirm no conflicts of interest.

\textbf{Cryptographic Lineage \& Validation.} This mathematical substrate has been cryptographically sealed and tracked on the global Sovereign Master Ledger to prevent retroactive editing and to verify the source authorship. The immutable SHA-256 integrity checksums, formal PDF renderings, and lineage authorities can be verified at \url{https://rdepaz.com/research}.

\medskip

\closing{Respectfully submitted,}
\end{letter}
\end{document}
