\documentclass[12pt, a4paper]{letter}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{amssymb}
\usepackage{hyperref}

\geometry{margin=1in}

\hypersetup{colorlinks=true, linkcolor=blue, urlcolor=blue}

\signature{Rafael D. De Paz \\ Independent Researcher \\ \texttt{me@rdepaz.com}}
\address{Rafael D. De Paz \\ Independent Researcher \\ \url{https://logos.pub}}

\begin{document}
\begin{letter}{Editorial Board \\ Systems \& Control Letters \\ Elsevier}

\opening{Dear Editors,}

I am writing to submit the enclosed manuscript, entitled

\begin{center}
\textbf{``The Calculus of Destiny: \\
Control Theory and Gradient Descent in \\
Underdetermined Human Trajectories,''}
\end{center}

\noindent for consideration for publication.

\medskip

\textbf{Summary.} The paper resolves the age-old philosophical paradox of determinism versus libertarian free will by formally modeling ``Destiny'' not as a pre-computed monolithic timeline, but as the mathematical \emph{global minimum of systemic friction} within a bounded state space ($G = \arg\min \text{Friction}(P)$). Using control theory and gradient descent optimization, I prove that an invariant teleological attractor (Destiny) is not only compatible with a non-deterministic stochastic controller (Free Will), but algorithmically relies upon it for execution.

\medskip

\textbf{Contributions.}
\begin{itemize}
  \item A formal mathematical definition of Destiny as a global minimum.
  \item Modeling biological lifespan as a non-deterministic differential equation: $dP/dt = f(P, G, W, \calL)$.
  \item Mathematical modeling of Grace as the negative gradient of the loss surface ($-\nabla \text{Friction}$).
  \item Implementation of the Crisis Resolution Matrix for modeling systemic trauma responses.
\end{itemize}

\medskip

This manuscript has not been previously published and is not under consideration at any other journal. I confirm no conflicts of interest.

\textbf{Cryptographic Lineage \& Validation.} This mathematical substrate has been cryptographically sealed and tracked on the global Sovereign Master Ledger to prevent retroactive editing and to verify the source authorship. The immutable SHA-256 integrity checksums, formal PDF renderings, and lineage authorities can be verified at \url{https://rdepaz.com/research} and \url{https://logos.pub}.

\medskip

\closing{Respectfully submitted,}
\end{letter}
\end{document}
